Age-related changes in plant growth and traits

### 2016-12-15 Analaysis-RA.Rmd
Renaming of files in Summary workflow; add starting commands for each analysis

@@

SummarySppAge[["mean"]]$leaf_shed_mean <- SummaryInd %>%
        group_by(species,age) %>%
        summarise(mean(leaf_shed_mean))

SummarySppAge[["mean"]]$leaf_replacement_mean <- SummaryInd %>%
        group_by(species,age) %>%
        summarise(mean(leaf_replacement_mean))

data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,total_inv,prop_surplus,
  growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
  LL_death,height_0,total_weight_0,all_leaf_inv,surplus_inv,all_leaf_and_repro_inv,propagule_inv,ovule_count,success_inv)
data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
data_ind <- select(SummaryInd,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv)

@@

```{r}
yvar <- "repro_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

yvar <- "repro_inv"
xvar <- "growth_leaf_pos"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

yvar <- "repro_inv"
xvar <- "all_leaf_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

```{r}
yvar <- "surplus_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

yvar <- "all_leaf_and_repro_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

yvar <- "all_leaf_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

yvar <- "ovule_count"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

>>>>

```{r}
# library(digest)
# library(Rcpp)
# library(reshape2)
# library(tibble)
library(smatr)
library(broom)
library(dplyr)
# library(stats)
# library(scales)
# library(colorspace)

remake::make("export")

SummaryCombine <- readRDS("export/SummaryCombine.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")

HarvestData <- readRDS("export/HarvestData.rds")
InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
PartsSummary <- readRDS("export/PartsSummary_all.rds")

source("R/figures.R")
```

@@

SummarySppAge[["mean"]]$leaf_shed_mean <- SummaryCombine %>%
        group_by(species,age) %>%
        summarise(mean(leaf_shed_mean))

SummarySppAge[["mean"]]$leaf_replacement_mean <- SummaryCombine %>%
        group_by(species,age) %>%
        summarise(mean(leaf_replacement_mean))

data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,total_inv,prop_surplus,
  growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
  LL_death,height_0,total_weight_0,all_leaf_inv,surplus_inv,all_leaf_and_repro_inv,propagule_inv,ovule_count,success_inv)
data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
data_ind <- select(SummaryCombine,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv)

@@

```{r}
yvar <- "repro_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)

@@

yvar <- "repro_inv"
xvar <- "growth_leaf_pos"
data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)

@@

yvar <- "repro_inv"
xvar <- "all_leaf_inv"
data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)

@@

```{r}
yvar <- "surplus_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)

@@

yvar <- "all_leaf_and_repro_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)

@@

yvar <- "all_leaf_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)

@@

yvar <- "ovule_count"
xvar <- "leaf_weight_0"
data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)

### 2016-12-15 Analysis-accessory.Rmd
Renaming of files in Summary workflow; add starting commands for each analysis

```{r}
library(digest)
library(Rcpp)
library(reshape2)
library(tibble)
library(smatr)
library(broom)
library(dplyr)
library(stats)
library(scales)
library(colorspace)

@@

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")
HarvestData <- readRDS("export/HarvestData.rds")
InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
PartsSummary <- readRDS("export/PartsSummary_all.rds")

>>>>

```{r}
# library(digest)
# library(Rcpp)
# library(reshape2)
# library(tibble)
library(smatr)
library(broom)
library(dplyr)
# library(stats)
# library(scales)
# library(colorspace)

@@

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")
